---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

# load package
library(tidyverse)
library(magick)
```

```{css}
body {
  padding: 50px
  background: #ecd2e0;
  font-family: "Lucida Console", "Courier New", monospace;
}

h2 {
  color: #f9f9f9;
  background-color: #424458;
  padding: 8px;
  border-radius: 15px;
  text-align: center;
}

h3 {
  color: #f9f9f9;
  background-color: #9699c7;
  padding: 8px;
  border-radius: 15px;
  text-align: center;
}

h4 {
  background-color: #ced1f8;
  padding: 8px;
  border-radius: 15px;
}

```

## TikTok Ad Personalization Analysis

This report presents the findings from the survey we created on how TikTok personalise ads based on user activity, including video interactions, searches, and past engagements with brands.

### The Dataset
The dataset used to create the summary values, and bar charts came from our survey. It consists of responses that came from observational logging.

```{r}
# data
csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQJkTb1AzZtdJ6tgBMZ4fMYp3HK1INAZQ4Mnx9RbkC2Lfh7TBvDXDUNS6YGLyreJzCAsUWD-OG9HYjd/pub?output=csv"

logged_data <- read_csv(csv_file)

# renaming variables
latest_data <- logged_data %>%
  rename(
    ad_length = 2,
    prior_search = 3,
    prior_interaction =  4,
    brand_awareness = 5,
    post_ad_action = 6,
    location_match = 7,
    ad_relevance = 8
  )

# picture of survey
survey_img <- image_read("survey.png") %>%
  image_scale(600)

# summary values
avg_ad_length <- mean(latest_data$ad_length)

avg_ad_relevance <- mean(latest_data$ad_relevance)

most_common_post_ad_action <- names(which.max(table(latest_data$post_ad_action)))

```

### **Survey**
This picture is a part of what the survey looks like.

`r survey_img`

### **Summary Values**
- **Average Ad Length:** `r avg_ad_length`
- **Average Ad Relevance Score:** `r avg_ad_relevance`
- **Most Common Post-Ad Action:** `r most_common_post_ad_action`


### **Bar Charts**

#### **Ad Relevance Score by Prior Search Behavior**

```{r}
# bar chart 2: Ad Relevance Score by Prior Search Behavior
bar_chart_2 <- latest_data %>%
  ggplot() +
  geom_bar(aes(x = ad_relevance, fill = prior_search)) +
  labs(title = "Ad Relevance Score by Prior Search Behavior",
       x = "Ad Relevance Score",
       y = "Count",
       fill = "Prior Search")
print(bar_chart_2)
```

#### **Ad Relevance Score by Brand Awareness**

```{r}
# bar chart 5: Ad Relevance Score by Brand Awareness
bar_chart_5 <- latest_data %>%
  ggplot() +
  geom_bar(aes(y = ad_relevance, fill = brand_awareness)) + 
  labs(title = "Ad Relevance Score by Brand Awareness",
       x = "Count",
       y = "Ad Relevance Score",
       fill = "Brand Awareness")

print(bar_chart_5)
```

#### **Post-Ad Actions by Prior Search Behavior**

```{r}
# bar chart 7: Post-Ad Actions by Prior Search Behavior
bar_chart_7 <- latest_data %>%
  ggplot() +
  geom_bar(aes(x = post_ad_action, fill = prior_search)) + 
  labs(title = "Post-Ad Actions by Prior Search Behavior",
       x = "Post-Ad Action",
       y = "Count",
       fill = "Prior Search")

print(bar_chart_7)
```
